Reviewers' comments from \textit{Immunity}

### 2017-11-27 paper/Immunity_reviews.tex
Added note to Reviewer 2 comment

1. Although mAb S139/1 is called a receptor binding site (RBS) antibody, the epitope is actually adjacent to the RBS. The abstract of the Yoshida paper called it "a novel conformational epitope adjacent to the receptor-binding domain of HA." It is not clear what a true RBS antibody (eg, 5J8, CH65) would do in this model.
{\color{red} We can certainly say that it binds \emph{near} the RBS rather than in the RBS.
I don't think it is worth adding additional antibodies at this time.}

>>>>

1. Although mAb S139/1 is called a receptor binding site (RBS) antibody, the epitope is actually adjacent to the RBS. The abstract of the Yoshida paper called it "a novel conformational epitope adjacent to the receptor-binding domain of HA." It is not clear what a true RBS antibody (eg, 5J8, CH65) would do in this model.
{\color{red} Although the three sites of escape found by Yoshida et al were indeed found to be near the RBS, they didn't crystallize the antibody in complex with HA. However, [Lee et al 2012 PNAS] published the crystal structure, and as can be seen in figure 1, the HCDR2 loop of S139/1 inserts into the receptor binding site.}
